Probe or Wait: Handling tail losses using Multipath TCP

### 2017-04-27 main.tex
Updates to sec VI

TCP has two mechanisms for detecting and recovering from packet loss: Fast Retransmit (FR) and Retransmission Timeout~(RTO)~\cite{Flach:2013}. 
Fast retransmit is triggered on receipt of a predecided number of duplicate acknowledgements, considering it as an indication of loss. In the case 
of RTO, a sender waits for the packet loss to trigger a timeout before retransmitting the packet. During such a timeout interval, 
the sender cannot retransmit any 
packets. However, with FR the out-of-order packets trigger duplicate acknowledgements. The sender can start retransmission of missing packets 
without waiting for a timeout. For flows where there are sufficiently many packets to be transferred, FR is quicker than RTO in detecting and 
recovering packet loss. During long flows, subsequent packets in the flow typically arrive at the receiver after a packet loss and based
on the duplicate acknowledgements that they trigger, FR coupled with fast recovery can quickly retransmit the missing data. 
On the other hand, shorter flows more frequently have to depend on RTO for packet loss detection and recovery, thus incurring more latency. A single 
packet loss in a short flow may take many RTTs to detect and recover. This scenario is also applicable to the packets at the end of the flow 
(or tail), of a long flow. Although RTO is reliable even in tail loss recovery, it is not efficient in terms of recovery completion time. Tail 
losses are one of the major causes of end-to-end latency detoriation in modern networks~\cite{Flach:2013}.

@@

Results comparing the burst completion time for new MPTCP TLP with that of TCP and MPTCP TLP for the considered cases are provided in 
Figure~\ref{mpnew}. In Figure~\ref{1pn}, MPTCP-New performs better than TCP in all scenarios, performs equal to MPTCP in symmetric scenarios and 
performs better than MPTCP in asymmetric scenarios with a lower delay on the alternate path. MPTCP-New achieves this improvement by retransmitting
 lost packet on the alternate path much before the RTO. It is also observed that there is no performance degradation when the alternate path has 
 higher delay. Probe packet on the primary path reaches faster than the retransmitted path and completes loss recovery at MPTCP level. In two packet 
 tail loss scenario as in Figure~\ref{2pn}, MPTCP-New performs better than TCP in all scenarios and better than MPTCP in all scenarios except when 
 the alternate path has a significantly higher delay than the original path, where performance is the same. In the single packet together with probe 
 loss scenario as in Figure~\ref{1ppn}, MPTCP-New performs better than both MPTCP and TCP in all scenarios with PTO triggering the probe retransmission
 on alternate path much earlier than the RTO.

>>>>

TCP has two mechanisms for detecting and recovering from packet loss: Fast Retransmit (FR) and Retransmission Timeout~(RTO)~\cite{Flach:2013}. 
Fast retransmit is triggered on receipt of a predecided number of duplicate acknowledgements, considering it as an indication of loss. In the case 
of RTO, a sender waits for the packet loss to trigger a timeout before retransmitting the packet. During such a timeout interval, 
the sender cannot retransmit any 
packets. However, with FR the out-of-order packets trigger duplicate acknowledgements. The sender can start retransmission of missing packets 
without waiting for a timeout. For flows where there are sufficiently many packets to be transferred, FR is quicker than RTO in detecting and 
recovering packet loss. During long flows, subsequent packets in the flow typically arrive at the receiver after a packet loss and based
on the duplicate acknowledgements that they trigger, FR coupled with fast recovery can quickly retransmit the missing data. 
On the other hand, shorter flows more frequently have to depend on RTO for packet loss detection and recovery, thus incurring more latency. A single 
packet loss in a short flow may take many RTTs to detect and recover. This scenario is also applicable to the packets at the end of the flow 
(or tail), of a long flow. Although RTO is reliable even in tail loss recovery, it is not efficient in terms of recovery completion time. Tail 
losses are one of the major causes of end-to-end latency deterioration in modern networks~\cite{Flach:2013}.

@@

Results comparing the burst completion time for new MPTCP TLP with that of TCP and MPTCP TLP for the considered cases are provided in 
Figure~\ref{mpnew}. In Figure~\ref{1pn}, MPTCP-New performs better than TCP in all scenarios, performs equal to MPTCP in symmetric scenarios and 
performs better than MPTCP in asymmetric scenarios with a lower delay on the alternate path. MPTCP-New achieves this improvement by retransmitting
 the lost packet on the alternate path much before the RTO. It is also observed that there is no performance degradation when the alternate path has 
 higher delay. The probe packet on the original path reaches faster than the retransmitted packet on the alternate path and completes loss recovery at the MPTCP level. In two packet 
 tail loss scenario as in Figure~\ref{2pn}, MPTCP-New performs better than TCP in all scenarios and better than MPTCP in all scenarios except when 
 the alternate path has a significantly higher delay than the original path, where performance is the same. For this scenario, MPTCP-New achieves
 this gain as the retransmission on the alternate path recovers the first lost packet and the probe packet on the original path recovers the
 second lost packet, and thus both lost packets can be recovered in parallel. 
 In the single packet together with probe 
 loss scenario as in Figure~\ref{1ppn}, MPTCP-New performs better than both MPTCP and TCP in all scenarios with PTO triggering the retransmission
 on the alternate path much earlier than the RTO.
